% --- LaTeX CV Template - S. Venkatraman ---

% Set document class and font size
\documentclass[letterpaper, 10pt]{article}
\usepackage[utf8]{inputenc}

% test
% Package imports
\usepackage{setspace, longtable, graphicx, hyphenat, hyperref, fancyhdr, ifthen, everypage, enumitem, amsmath, setspace}

% --- Page layout settings ---

% Set page margins
\usepackage[left=0.5in, right=0.5in, bottom=0.7in, top=0.5in]{geometry}

% Set line spacing
\renewcommand{\baselinestretch}{1.15}

% --- Page formatting ---

% Set link colors
\usepackage[dvipsnames]{xcolor}
\hypersetup{colorlinks=true, linkcolor=RoyalBlue, urlcolor=RoyalBlue}

% Set font to Libertine, including math support
%\usepackage{libertine}
\usepackage[libertine]{newtxmath}

% Remove page numbering
\pagenumbering{gobble}


\usepackage{csquotes}

% --- Document starts here ---

\begin{document}

% Name and date of last update to this document
%\noindent{\textbf{Tiannuo Yang}
%\hfill{\it\footnotesize Updated \today}}


% --- Contact information and other items ---

%\vspace{0.5cm} 
%\begin{center}
%\begin{tabular}{lll}
%% Line 1: Email, GitHub, office location
%\textbf{Email}: email@cornell.edu      &
%\hspace{0.55in} \textbf{GitHub}: //github-username    &
%\hspace{0.4in} 	\textbf{Office}: Your Building 101 \\
%
%% Line 2: Phone number, LinkedIn, citizenship
%\textbf{Phone}: (314) 159-2654   & 
%\hspace{0.55in} \textbf{LinkedIn}: //LinkedIn-URL   & 
%\hspace{0.4in} \textbf{Citizenship}: Country 
%\end{tabular}
%\end{center}

% --- Start the two-column table storing the main content ---

% Set spacing between columns
\setlength{\tabcolsep}{.01\textwidth}

% Set the width of each column
\begin{longtable}{p{.14\textwidth}p{.75\textwidth}}

\textbf{Tiannuo Yang} & \hfill{\it\footnotesize Updated \today} \\
\hline \\


% --- Section: Contact Information --

\textcolor{OliveGreen}{Contact} & Ginsburg Hall (GCS), 1031 Downey Way \hfill tnyang2000@gmail.com \\
\textcolor{OliveGreen}{Information} & Los Angeles, CA 90089 \hfill  \url{https://tiannuo-yang.github.io/} \\
& \\


% --- Section: Research interests ---

\nohyphens{\textcolor{OliveGreen}{Research Interests}}
& I am broadly interested in AI systems, especially generative AI such as LLMs, RAG, agents, and world models. I advocate for AI for all. Overall, my research is about two questions: how to understand efficiency insights underneath groundbreaking AI techs; and how to supercharge AI deployment in practice with full-stack designs?
\vspace{0.01\textwidth} \\

& To this end, I like to collaborate with AI people. Check out our latest work, SearchAgent-X, a collaboration with the Search-R1 team, on how to accelerate cutting-edge LLM search agents!\\
& \\


% --- Section: Education ---

\textcolor{OliveGreen}{Education} 
& \textbf{University of Southern California}, Los Angeles, CA, United States \\
& \textcolor[RGB]{200, 0, 0}{\textit{Ph.D. Student in Computer Science}} \hfill from August 2025 \\
& Advisor: Willie Neiswanger \vspace{0.01\textwidth} \\

& \textbf{Nankai University}, Tianjin, China \\ 
& \textit{Master in Computer Science} (Exempted from Entrance Exam) \hfill August 2022 -- Present \\
& Advisor: Professor Yusen Li \hspace{0.04\textwidth} GPA: \textit{3.63/4.0} \\
& Thesis: Automated Performance Tuning Techniques for Parallel Applications \vspace{0.01\textwidth} \\

& \textbf{University of Science and Technology Beijing}, Beijing, China \\ 
& \textit{Bachelor in Information Management and Information System} \hfill August 2018 -- June 2022 \\
& Major GPA: \textit{3.97/4.0} \hspace{0.04\textwidth} Cumulative GPA: \textit{3.89/4.0}
\vspace{0.01\textwidth} \\

& \textbf{Southern Taiwan University of Science and Technology}, Taiwan, China \\ 
& \textit{Major in Information Management} (Exchange Program) \hfill September 2019 -- January 2020 \\
& Cumulative GPA: \textit{4.3/4.3} \\
& \\

% --- Section: Research Experiences ---
\textcolor{OliveGreen}{Research}
& \textbf{University of Illinois at Urbana-Champaign}, Urbana, IL, United States \\ 
\textcolor{OliveGreen}{Experience} & \textit{Retrieval-Augmented Generation} \hfill May 2024 -- Present \\
&  Working with Professor Minjia Zhang on GPU-enhanced retrieval augmented generation, shedding lights on key concerns like batching strategies and
latency-quality tradeoffs.
\vspace{0.01\textwidth} \\


& \textbf{Nankai University}, Tianjin, China \\ 
& \textit{Datacenter, System, Machine Learning for System} \hfill August 2022 -- Present \\
&  Working with Professor Yusen Li on automatic performance tuning and hardware resource isolation for job collocations within multi-core systems.
\vspace{0.01\textwidth} \\


& \textbf{Ant Group}, Beijing, China \\ 
& \textit{Vector Retrieval, Vector Database Optimization} \hfill June 2023 -- January 2024 \\
&  Worked as a research intern under Dr. Jianguo Li and Wen Hu on optimizing AI infrastructure - vector database, enhancing CodeFuse services (a coding large language model platform).
\vspace{0.01\textwidth} \\


& \textbf{University of Chinese Academy of Sciences}, Beijing, China \\ 
& \textit{Mixed Integer Programming, Heuristic Algorithm} \hfill September 2020 -- September 2021 \\
&  Worked as an undergraduate research assistant under Professor Guanghui Zhou to develop data-driven combinatorial optimization problem (vehicle routing optimization). \\
& \\


% --- Uncomment the next few lines if you want to include some courses ---
%& \textbf{Selected coursework}
%\begin{itemize}[noitemsep,leftmargin=*]
%\item \underline{Relevant subject 1}: Course 1, Course 2, Course 3, Course 4
%\item \underline{Relevant subject 2}: Course 1, Course 2, Course 3, Course 4
%\end{itemize} \\


% --- Section: Publications ---
\nohyphens{\textcolor{OliveGreen}{Publications}} 
& \textbf{Supercharging AI Systems} 
\vspace{0.01\textwidth} \\

& \textit{$^*$Denotes equal contribution. $^\dagger$Denotes corresponding authorship.} 
\vspace{0.01\textwidth} \\

& \underline{T. Yang}, Z. Yao, B. Jin, L. Cui, Y. Li, G. Wang, X. Liu. \enquote{Demystifying and Enhancing the Efficiency of Large Language Model Based Search Agents.} \textit{arXiv}, 2025
\vspace{0.01\textwidth} \\

& K. Cheng, Z. Wang, W. Hu, \underline{T. Yang}, J. Li, S. Zhang. \enquote{SCOOT: Towards SLO-Optimized LLM Serving via Automatic Inference Engine Tuning.} \textit{The Web Conference (WWW)}, 2025. \textcolor[RGB]{200, 0, 0}{Oral Presentation.}
\vspace{0.01\textwidth} \\

& \underline{T. Yang}, W. Hu, W. Peng, Y. Li, J. Li, X. Liu, G. Wang. \enquote{VDTuner: Automated Performance Tuning for Vector Data Management Systems.} \textit{International Conference on Data Engineering (ICDE)}, 2024. \textcolor[RGB]{200, 0, 0}{Deployment on Ant Group's CodeFuse platform.}
\vspace{0.01\textwidth} \\

& \underline{T. Yang}, R. Chen, Y. Li, X. Liu, G. Wang. \enquote{CoTuner: A Hierarchical Learning Framework for Coordinately Optimizing Resource Partitioning and Parameter Tuning.} \textit{International Conference on Parallel Processing (ICPP)}, 2023.
\vspace{0.01\textwidth} \\

& \textbf{Research Survey} 
\vspace{0.01\textwidth} \\

& Y. Zhou$^*$, X. Lin$^*$, X. Zhang$^*$, M. Wang$^*$, G. Jiang$^*$, H. Lu$^*$, Y. Wu$^*$, K. Zhang$^*$, Z. Yang$^*$, K. Wang$^*$, Y. Sui$^*$, F. Jia$^*$ Z. Tang$^*$, Y. Zhao$^*$, H. Zhang$^*$, \underline{T. Yang}$^*$, W. Chen$^*$, Y. Mao$^*$, Y. Li$^*$, D. Bao$^*$, Y. Li$^*$, H. Liao$^*$, T. Liu$^*$, J. Liu$^*$, J. Guo$^*$, X. Zhao, Y. WEI, H. Qian, Q. Liu, X. Wang, W.K. Chan, C. Li, Y. Li, S. Yang, J. Yan, C. Mou, S. Han, W. Jin, G. Zhang, X. Zeng. \enquote{On the Opportunities of Green Computing: A Survey.} \textit{arXiv}, 2023 \\
& (Writing Section: 6.4 Resource Optimization). 
\vspace{0.01\textwidth} \\

& \textbf{Operations Research (Undergraduate Thesis)}
\vspace{0.01\textwidth} \\

& \underline{T. Yang}$^\dagger$, Z. Chu, B. Wang. \enquote{Feasibility on the Integration of Passenger and Freight Transportation in Rural Areas: A Service Mode and an Optimization Model.} \textit{Socio-Economic Planning Sciences} (SCI JCR Q1), 2023. \\
& \\


% --- Section: Projects ---
\nohyphens{\textcolor{OliveGreen}{Research}}
& {Qiyuan Laboratory Innovation Fund} \hfill  November 2023 -- November 2024 \\
\nohyphens{\textcolor{OliveGreen}{Projects}}
& Worked as a core member on resource isolation mechanism for a multi-tenant cache system (i.e., Cachelib by Facebook).
\vspace{0.01\textwidth} \\

& {CCF-Ant Research Fund on Green Computing} \hfill January 2023 -- January 2024 \\
& Worked as a leader to write project proposal and conclusion, conduct research on AI infrastructure (vector database optimization) and practical platform deployment.
\vspace{0.01\textwidth} \\

& {National Natural Science Foundation (NSF) of China} \hfill January 2023 -- Present \\
& Working as a core member on improving resource utilization in cloud with QoS guarantee. \vspace{0.01\textwidth} \\

& {Major Project of National NSF of China} \hfill December 2022 -- Present \\
& Working on real-time scheduling of cluster robots for major equipment manufacturing. \\
& \\


% --- Section: Honors ---

%\nohyphens{\textcolor{OliveGreen}{Academic}}
%& 1st National Massive Storage Competition \hfill June 2023 \\
%\nohyphens{\textcolor{OliveGreen}{Competitions}}
%& \textit{Scheduling of Storage Data Retrieval Tasks} \hfill National 3rd Prize
%\vspace{0.01\textwidth} \\
%
%& 7th National ‘Internet+’ Innovation and Entrepreneurship Competition \hfill December 2021 \\
%& \textit{Intelligent Tuning of Cloud Services (Industrial track)} \hfill Provincial Gold Prize
%\vspace{0.01\textwidth} \\
%
%& National Contemporary Undergraduate Mathematical Contest \hfill November 2020 \\
%& \textit{Mixed Integer Programming and Heuristic Algorithms} \hfill National 2nd Prize (top 3.6\%) \\
%& \\


% --- Section: Honors ---

\nohyphens{\textcolor{OliveGreen}{Honors And}}
& Ph.D. Student Fellowship, USC \hfill 2025 \\
\nohyphens{\textcolor{OliveGreen}{Awards}}
& Excellent Graduate, Nankai University (\textcolor[RGB]{200, 0, 0}{8 out of 157}) \hfill 2025 \\
& 1st-Class Gongneng Scholarship, Nankai University \hfill 2023, 2024 \\
& National 3rd Prize, Massive Storage Competition \hfill 2022 \\
% & Provincial Gold Prize, 'Internet+' Innovation and Entrepreneurship Competition \hfill 2021 \\
% & Excellent Student, University of Science and Technology Beijing (USTB) \hfill 2020 \\
& National 2nd Prize (\textcolor[RGB]{200, 0, 0}{1493/41826 = top 3.6\%}), Contemporary Undergraduate Mathematical Contest in Modeling \hfill 2020 \\
% & 2nd Place, Marketing Competition (turnover RMB 20,000+), USTB \hfill 2020 \\
& Top Ten Singers on Campus, USTB \hfill 2020 \\
% & Professional Certification in E-Commerce, Taiwan Computer Skills Foundation (CSF) \hfill 2019 \\
% & Certification of Enterprise Electronic Assistant Planner, Taiwan CSF \hfill 2019 \\	
% & Team Gold Award, College Students' Social Practice, USTB \hfill 2019 \\
& \\
 

% --- Section: Talks and Services ---
\nohyphens{\textcolor{OliveGreen}{Talks And}}
& \textbf{Invited talk} on "Towards Efficient LLM Search Agents" \\
\nohyphens{\textcolor{OliveGreen}{Services}} 
& \quad\quad by Di Wu, at ByteDance, June 6th 2025 \\
& \quad\quad at MLSys Reading Group, Nankai University, June 5th 2025 \\
& \quad\quad by Haosen Shi, at CUHK, June 4th 2025 
\vspace{0.01\textwidth} \\

& \textbf{Conference Talk} at \\
& \quad\quad the 40th ICDE at Utrecht, the Netherlands, May 2024 \\
& \quad\quad the 52nd ICPP, Online, August 2023
\vspace{0.01\textwidth} \\

& \textbf{Reading Group Founder and Leader} for \\
& \quad\quad Machine learning system research at Nankai-Baidu Joint Lab (from October 2024)
\vspace{0.01\textwidth} \\

& \textbf{Reviewer} for \\
& \quad\quad the 2025 ACM Web Conference\\
& \\

% --- Section: Software And Systems ---
\nohyphens{\textcolor{OliveGreen}{Open Source}}
& SearchAgent-X: Highly efficient system for reasoning-search interleaved LLM agents. \\
& \url{https://github.com/tiannuo-yang/SearchAgent-X}
\vspace{0.01\textwidth} \\

& VDTuner: Automated performance tuning framework for vector data management systems. \\
& \url{https://github.com/tiannuo-yang/VDTuner} \\
& (Chinese Blog: \url{https://mp.weixin.qq.com/s/1JgXM5WSWBTv7fA0TLGfqw})
\vspace{0.01\textwidth} \\

& G-VRP-IPD-TW: Mathematical model and real-world dataset for a complex combinatorial optimization problem in transportation. \\
& \url{https://github.com/tiannuo-yang/G-VRP-IPD-TW} \\


\end{longtable}
\end{document}
